Temporal Developer Concept Witchery: Latent Dirichlet Allocation Applied to Revisions

### 2009-02-17 presentation/presentation.out.tex
transitive closure diagram

\sslide{Introduction}
\begin{itemize}
\item Intro

@@

\end{itemize}
\end{slide}

>>>>

\sslide{Introduction}
\begin{itemize}
\item Stakeholders want to know what the focus of the last iteration was
\item Evidence of work done at Retrospective meetings
\item Difference between developer opinion and developer commits

\end{itemize}
\sslide{Topic Clustering }
\begin{itemize}
\item Need to track continuous topics across 
\item Similarity between topics
\item Clusters of the transitive closure of topics with X\% similarity
	\begin{itemize}
	\item Fill flood along similarity, make subsets of everyone who X\% similar to any of their neighbors, make that a cluster

%\igbigslidecap{transitiveclosure}{Clustering topics (black dots) by Transitive Closure based on similarity (arcs)}

\begin{center}
\includegraphics[width=\textwidth]{transitiveclosure}
Clustering topics (black dots) by Transitive Closure based on similarity (arcs)
\end{center}

@@

\end{itemize}
\end{itemize}
\end{slide}

### 2009-02-17 presentation/presentation.tex
transitive closure diagram

\sslide{Introduction}
\begin{itemize}
\item Intro

@@

\end{itemize}
\end{slide}

>>>>

=Introduction
* Stakeholders want to know what the focus of the last iteration was
* Evidence of work done at Retrospective meetings
* Difference between developer opinion and developer commits

=Topic Clustering 
* Need to track continuous topics across 
* Similarity between topics
* Clusters of the transitive closure of topics with X\% similarity
** Fill flood along similarity, make subsets of everyone who X\% similar to any of their neighbors, make that a cluster

%\igbigslidecap{transitiveclosure}{Clustering topics (black dots) by Transitive Closure based on similarity (arcs)}

\begin{center}
\includegraphics[width=\textwidth]{transitiveclosure}
Clustering topics (black dots) by Transitive Closure based on similarity (arcs)
\end{center}

@@

=
\end{slide}
